---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(sqlr)
```

# sqlr

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/giperbio/sqlr/workflows/R-CMD-check/badge.svg)](https://github.com/giperbio/sqlr/actions)
[![Codecov test coverage](https://codecov.io/gh/giperbio/sqlr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/giperbio/sqlr?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](https://giperbio.github.io/sqlr/CODE_OF_CONDUCT.html)
<!-- badges: end -->

## Overview

`sqlr` is an R package that provides a system to produce systematic quantitative literature reviews, a systematic review method presented by Catherine Pickering and Jason Byrne in [2014](https://doi.org/10.1080/07294360.2013.841651). Its aim is to facilitate the work of PhD candidates and other early-career researchers with evidence synthesis and to improve reproducibility in research.

Learn more about systematic quantitative literature reviews [here](https://www.griffith.edu.au/griffith-sciences/school-environment-science/research/systematic-quantitative-literature-review).

## Installation

You can install `sqlr` with:

``` {r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("giperbio/sqlr")
```

## Citation

If you use `sqlr` in your research, please consider citing it. We put a lot of work to build and maintain a free and open-source R package. You can find the citation below.

```{r}
citation("sqlr")
```

## Contributing

We welcome contributions, including bug reports.

Take a moment to review our [Guidelines for Contributing](https://giperbio.github.io/sqlr/CONTRIBUTING.html).

<br>

Become an `sqlr` supporter!

Click [here](https://github.com/sponsors/danielvartan) to make a donation. Please indicate the `sqlr` package in your donation message.
